A finite-state morphological transducer for Kyrgyz

### 2012-03-13 paper/paper.tex
more updates

The analyser is designed to be used with the longest-match left-to-right (LRLM) tokenisation strategy, as described in \cite{garrido-alenda02}. Thus when more than one `word' needs to be output, they are joined with the \texttt{+} symbol, which is reserved for joining two `words' in one analysis, e.g. {\em өнүктүрөбүзбү} `TRANSLATION' is analysed as 
{\tt өнүк<v><tv><caus><aor><p1><pl>+бы<mod_qst>}

>>>>

The analyser is designed to be used with the longest-match left-to-right (LRLM) tokenisation strategy, as described in \cite{garrido-alenda02}. Thus when more than one `word' needs to be output, they are joined with the \texttt{+} symbol, which is reserved for joining two `words' in one analysis, e.g. `өнүктүрөбүзбү' {\em TRANSLATION} is analysed as 
өнүк{\tt {\small <v><tv><caus><aor><p1><pl>+}}бы{\tt {\small <qst>}} two words: `өнүк' (verb, transitive, causative, aorist, first person, plural) and `бы' (question clitic).
